### 2021-04-27 conclusion.tex
behavior > behaviour
Use American English consistently.
As suggested by Grammarly.

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help design new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of an ATP with random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these patterns in a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}

>>>>

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help design new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviors of an ATP with random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behavior as perceived by a human observer.
The challenge is to extract these patterns in a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}
